---
output: html_document
params:
  J:            NA
  alpha:        NA
  beta:         NA
  delta:        NA
  sigma0:       NA
  sigma1:       NA
  ratio:        NA
  shape:        NA
  optimality:   NA
  quantile_sub: NA
  integer_n:    NA
  n0:           NA
  n1:           NA
  n:            NA
  e:            NA
  f:            NA
  opchar:       NA
  plots:        NA
  estimators:   NA
---

```{r setup, include = F}
knitr::opts_chunk$set(echo    = F,
                      results = "asis")
```

#### Design setting

The trial will be designed to compare an experimental treatment (arm 1) to a control (arm 0), through a group-sequential trial with at most $J$ stages. Response $X_{ijk}$, from patient $i=1,\dots,n_k$, in arm $k=0,1$, in stage $j=1,\dots,J$, will be assumed to be distributed as $X_{ijk} \sim N(\mu_k,\sigma_k^2)$. Then, the hypothesis to be tested will be:
$$ H_0 : \tau = \mu_1 - \mu_0 \le 0.$$
The type-I error-rate will be desired to be at most $\alpha$, and the trial will be powered at level $1-\beta$ for the scenario where $\tau=\delta>0$ (the *alternative hypothesis* $H_1$).

At interim analysis $j=1,\dots,J$, a standardised test statistic $Z_j$ will be
compared to efficacy and futility boundaries $e_j$ and $f_j$ respectively.

#### Inputs

```{r, echo = F, results = "asis"}
  J            <- params$J
  alpha        <- params$alpha
  beta         <- params$beta
  delta        <- params$delta
  sigma0       <- params$sigma0
  sigma1       <- params$sigma1
  ratio        <- params$ratio
  shape        <- params$shape
  optimality   <- params$optimality
  quantile_sub <- params$quantile_sub
  integer_n    <- params$integer_n
  n0           <- params$n0
  n1           <- params$n1
  e            <- params$e
  f            <- params$f
  opchar       <- params$opchar
  plots        <- params$plots
  estimators   <- params$estimators
```
  
```{r, echo = F, results = "asis"}
if (shape == "haybittle_peto") {
  shape_text        <- "Haybittle-Peto"
} else if (shape == "near_optimal") {
  shape_text        <- "Near-optimal"
} else if (shape == "power_family") {
  shape_text        <- "Power-family"
} else if (shape == "triangular") {
  shape_text        <- "Triangular-test"
} else if (shape == "wang_tsiatis") {
  shape_text        <- "Wang-Tsiatis"
} else if (shape == "obrien_fleming") {
  shape_text        <- "O'Brien-Fleming"
} else if (shape == "pocock") {
  shape_text        <- "Pocock"
} 

if (shape == "near_optimal") {
  if (optimality == "null_optimal") {
    optimality_text <- "be to minimise the expected sample size under the null"
  } else if (optimality == "alt_optimal") {
    optimality_text <- "be to minimise the expected sample size under the alternative"
  } else if (optimality == "delta_minimax") {
    optimality_text <- "be to minimise the maximum expected sample size"
  } else if (optimality == "balanced") {
    optimality_text <- "be a balanced near-optimal design"
  }
} else {
  optimality_text <- "not be used (i.e., a non-optimised design has been chosen)"
}

if (quantile_sub) {
  quantile_sub_text <- "will"
} else {
  quantile_sub_text <- "will not"
}

if (integer_n) {
  integer_n_text    <- "will"
} else {
  integer_n_text    <- "will not"
}

if (plots) {
  plot_text         <- "will"
} else {
  plot_text         <- "will not"
}

if (estimators) {
  estimator_text         <- "will"
} else {
  estimator_text         <- "will not"
}
```

The following choices were made:

- A maximum of $J = \boldsymbol{`r J`}$ stages will be allowed in the trial.
- The desired type-I error-rate will be $\alpha = \boldsymbol{`r alpha`}$.
- The desired type-II error-rate will be $\alpha = \boldsymbol{`r beta`}$.
- The trial will be powered for $\delta = \boldsymbol{`r delta`}$.
- The standard deviation of the responses in the control arm will be assumed to be: $\sigma_0 = \boldsymbol{`r sigma0`}$.
- The standard deviation of the responses in the experimetnal arm will be assumed to be: $\sigma_1 = \boldsymbol{`r sigma1`}$.
- The allocation ratio to the experimental arm relative to the control arm will be: $r = \boldsymbol{`r ratio`)}$.
- __`r shape_text`__ boundaries will be calculated.
- The optimality criteria will __`r optimality_text`__.
- Quantile substitution __`r integer_n_text`__ be used.
- The sample size in each arm __`r integer_n_text`__ be required to be an integer.
- Plots __`r plot_text`__ be produced.
- Estimator performance __`r estimator_text`__ be evaluated (currently only available for two-stage designs).

#### Outputs

```{r, echo = F, results = "asis"}
typeI  <- round(opchar[1, 2], 3)
typeII <- round(1 - opchar[3, 2], 3)
e_text <- paste0("(", paste(round(e, 3), collapse = ", "), ")")
f_text <- paste0("(", paste(round(f, 3), collapse = ", "), ")")
```

- The required stage-wise group size in the control arm is: $n_0 = \boldsymbol{`r round(n0, 3)`}$.
- The required stage-wise group size in the experimental arm is: $n_1 = \boldsymbol{`r round(n1, 3)`}$.
- The type-I error-rate is: $\boldsymbol{`r typeI`}$.
- The type-II error-rate is: $\boldsymbol{`r typeII`}$.
- The following efficacy boundaries should be used: $\boldsymbol{`r e_text`}$.
- The following futility boundaries should be used: $\boldsymbol{`r f_text`}$.

